---
title: "Simulation Results"
author: "Bianca Brusco"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,cache=TRUE)
source(here::here("src/print_sim20230725_results.R"))
```


Differences from last time:

- Estimate the covariance parameters used in kriging via `likfit` instead of using the `geoR:variofit` function. The initial values for likfit are $\sigma_{\eta}$ and $\phi_{\eta}$ (the real ones).  
- Made $\beta1$ smaller: 1.2. 
- Reduced SIGMA2X from 3 to 0.2. 
- FEVD: change estimation method from Maximum Likelihood to Generalize Maximum Likelihood. 
- currently just looking at B=3,1,0. 

(MLE seemed to sometimes non find the correct max -- see end of this document for example). 


**True values**:

Stations Population Size = 400 stations

```
SIGMA2 = 0.1. 
PHI =  0.6. 
SIGMA2X = 0.2. 
BETA1 = 1.2. 
```

Currently showing results for 50 simulations for PHIX = 0.2, 0.5, 1. 
Sample sizes are 120 and 280

## Results for PHI-X = 0.2


```{r}
PHIX <- 0.2
```

### Sample Size: 120

```{r,echo=FALSE}
SAMPLE_SIZE <- 120
print_results()

```


### Sample Size: 280

```{r,echo=FALSE}
SAMPLE_SIZE <- 280
print_results()
```


\newpage

## Results for PHI-X = 0.5

```{r}
PHIX <- 0.5
```

### Sample Size: 120

```{r,echo=FALSE}
SAMPLE_SIZE <- 120
print_results()
```


### Sample Size: 280

```{r,echo=FALSE}
SAMPLE_SIZE <- 280
print_results()
```

\newpage

## Results forFOR PHI-X = 1

```{r}
PHIX <- 1
```

### Sample Size: 120

```{r,echo=FALSE}
SAMPLE_SIZE <- 120
print_results()
```


### Sample Size: 280

```{r,echo=FALSE}
SAMPLE_SIZE <- 280
print_results()
```



# Example of MLE method failing:

IF using fevd: location estimated to -1201


```{r}
# 
# bad_stat <- 304
# 
# stat_dat <- true_data %>% filter(station==bad_stat)
# fit <- fevd(stat_dat$value, method="MLE")

############################################
# fevd(x = stat_dat$value, method = "MLE")
# 
# [1] "Estimation Method used: MLE"
# 
# 
# Negative Log-Likelihood Value:  807.7038 
# 
# 
# Estimated parameters:
#   location     scale     shape 
# -1201.703  3662.540  3167.249 
# 
# AIC = 1621.408 
# 
# BIC = 1627.144 



#fit2 <- fevd(stat_dat$value, method="GMLE")
# fevd(x = stat_dat$value, method = "GMLE")
# 
# [1] "Estimation Method used: GMLE"
# 
# 
# Negative Log-Likelihood Value:  136.8874 
# 
# 
# Estimated parameters:
#   location      scale      shape 
# -1.2047879  0.7069493  0.4994669 
# 
# AIC = 279.7749 
# 
# BIC = 285.5109 
```